Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-10 WSSSPE4_report/WSSSPE4_report.tex
fixing numbers of submission and lightning talks

Submissions to WSSSPE4 comprised
20 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
Specifically,
18 lightning talks,
4 idea papers,
3 position papers,
2 experience papers,
and
3 demos
were accepted.
The papers are discussed in Section~\ref{sec:papers},
and the lightning talks are discussed in Section~\ref{sec:lightning}.
The paper and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

The 12 excellent submissions resulted in 10-min talks (four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. They covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}

@@

There were 18 \katznote{this is what I found on EasyChair and wrote in \S2, but I think there are 16 listed below.  I wonder what the difference is?} lightning talks presented at WSSSPE4, as follows.
%
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
%
\begin{itemize}[itemsep=1ex]
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Sufi, Community Lead at the Software Sustainability Institute (SSI), discussed
    the SSI Fellowship program and the fellows, including their
    demographic breakdown and domains of practice. This program came about
    based on the institute's desire to integrate with the research community---thus
    inspiring change from within---rather than preach to it. Five SSI fellows
    attended WSSSPE4.

>>>>

Submissions to WSSSPE4 comprised
18 lightning talks,
4 idea papers,
3 position paper,
5 experience papers,
and
3 demos.
Most of the submissions were accepted, since the goal of WSSSPE is always to
take in as many relevant inputs as possible, and to encourage their authors to
participate in sharing and implementing their ideas.
Specifically,
16 lightning talks,
4 idea papers,
3 position papers,
2 experience papers,
and
3 demos
were accepted.
The papers are discussed in Section~\ref{sec:papers},
and the lightning talks are discussed in Section~\ref{sec:lightning}.
The paper and lightning talks have been published as a volume in the CEUR Workshop Proceedings~\cite{WSSSPE4-proceedings}.

@@

WSSSPE included the presentation of 12 10-minute talks (based on four idea papers, three position papers,
two experience papers, and three demos) that addressed a wide range of topics around
sustainability for software in science. They covered three main areas:
\begin{enumerate}
\item The specifics of the academic environment for software development and for so-called
research programmers or research software engineers;
\item The characteristics and needs of research software in general such as the lifecycle of
software in science, preservation, curation, sharing, and reproducibility challenges; and
\item Lessons learned from or visions for use cases of scientific software and communities
working with and\slash or on a software package.
\end{enumerate}

@@

There were 16 lightning talks presented at WSSSPE4, as follows.
%
A \textsuperscript{\textasteriskcentered} indicates which author presented the
lightning talk, for those with multiple authors.
%
\begin{itemize}[itemsep=1ex]
    \item \textbf{Shoaib Sufi: \emph{The Software Sustainability Institute Fellowship
    programme; supporting the social side of research software}}~\cite{Sufi:2016ws}.
    Sufi, Community Lead at the Software Sustainability Institute (SSI), discussed
    the SSI Fellowship program and the fellows, including their
    demographic breakdown and domains of practice. This program came about
    based on the institute's desire to integrate with the research community---thus
    inspiring change from within---rather than preach to it. Five SSI fellows
    attended WSSSPE4.
